### 2020-05-29 writeup/experiments.tex
taskonomy results

\subsection{Validating Theoretical Observations}

@@

>>>>

\subsection{Validating Theoretical Implications}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{c c c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
		& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
		% {\bf CNN}  & 76\% & - & 32\% & -\\
		\bottomrule
		\end{tabular}
	\end{center}
	\caption{Taskonomy experiment.}
	\label{tab:taskonomy}
	\end{table}
